---
title: rapport BIO500

author:
  - name: Éloïse Paquette, Danaé Vaillancourt, Élodie Michel et Camille Breton

lineno: false

output: pdf_document

---


Introduction {.unnumbered}
========================================

Please note that whilst this template provides a preview of the typeset
manuscript for submission, to help in this preparation, it will not
necessarily be the final publication layout. For more detailed
information please see the [PNAS Information for
Authors](http://www.pnas.org/site/authors/format.xhtml).


Méthode {#author-affiliations .unnumbered}
-------------------

Include department, institution, and complete address, with the
ZIP/postal code, for each author. Use lower case letters to match
authors with institutions, as shown in the example. Authors with an
ORCID ID may supply this information at submission.

Résultats {#submitting-manuscripts .unnumbered}
----------------------

Voici l'évolution de la richesse spécifique à travers le temps :

```{r fig.richesse, echo=FALSE, out.width="0.9\\linewidth", fig.cap="Richesse spécifique selon le temps"}
fig_rich <- tar_read(figure_richesse)
knitr::include_graphics(fig_rich)
```


```{r phenologie, echo=FALSE, fig.cap="Phénologie des espèces les plus observées", out.width='100%'}
fig_pheno <- tar_read(figure_phenologie)
knitr::include_graphics(fig_pheno)
```
Discussion {#format .unnumbered}
------

Many authors find it useful to organize their manuscripts with the
following order of sections; Title, Author Affiliation, Keywords,
Abstract, Significance Statement, Results, Discussion, Materials and
methods, Acknowledgments, and References. Other orders and headings are
permitted.

conclusion {#manuscript-length .unnumbered}
-----------------

PNAS generally uses a two-column format averaging 67 characters,
including spaces, per line. The maximum length of a Direct Submission
research article is six pages and a PNAS PLUS research article is ten
pages including all text, spaces, and the number of characters displaced
by figures, tables, and equations. When submitting tables, figures,
and/or equations in addition to text, keep the text for your manuscript
under 39,000 characters (including spaces) for Direct Submissions and
72,000 characters (including spaces) for PNAS PLUS.
x
